\newcommand{\TypecaseDesc}{Cast guarded with \code{instanceof}, class literal, or application-specific tag.}
\newcommand{\EqualsDesc}{A cast used in the implementation of the well-known \code{equals} method.}
\newcommand{\FamilyDesc}{A cast applied in a family of classes.}
\newcommand{\FactoryDesc}{A cast used to convert a newly created object.}
\newcommand{\KnownReturnTypeDesc}{The client of an API knows the exact return type of a method invocation.}
\newcommand{\DeserializationDesc}{A cast used to convert newly created objects in deserialization.}
\newcommand{\ParserStackDesc}{A cast to an heterogenous stack.}
\newcommand{\CompositeDesc}{A composite cast.}
\newcommand{\StashDesc}{A cast to an heterogenous collection element.}
\newcommand{\ObjectAsArrayDesc}{A cast to a constant array slot used as a field of an object.}
\newcommand{\SelectOverloadDesc}{A cast to disambiguate between overloaded methods.}
\newcommand{\AccessSuperclassFieldDesc}{A cast to access a private field in a superclass.}
\newcommand{\CovariantReturnTypeDesc}{A cast when the return type of a method is covariant.}
\newcommand{\CovariantGenericDesc}{Remove type parameter or an upcast to permit covariant generics.}
\newcommand{\ImplicitIntersectionTypeDesc}{A cast to implicitly use an intersection type.}
\newcommand{\SoleSubclassImplementationDesc}{A cast to the only subclass implementation.}
\newcommand{\FluentAPIDesc}{Cast to permit a fluent API through method chaining.}
\newcommand{\NewDynamicInstanceDesc}{Cast the result of \code{newInstance} in \code{Class}, \code{Constructor}, or \code{Array}.}
\newcommand{\ReflectiveAccessibilityDesc}{Cast the result of the \code{Method::invoke} or \code{Field::get}.}
\newcommand{\GenericArrayDesc}{A cast to create a generic array.}
\newcommand{\UnoccupiedTypeParameterDesc}{A cast used to change an unoccupied type parameter in a generic type.}
\newcommand{\UseRawTypeDesc}{A cast to a raw type (instead of using the generic type).}
\newcommand{\RemoveWildcardDesc}{A cast to remove a wildcard in a generic type.}
\newcommand{\RedundantDesc}{A cast that is not necessary for compilation.}
\newcommand{\VariableSupertypeDesc}{A cast to a variable that could be declared to be more specific.}

\newcommand{\gGuardedTableDesc}{The cast patterns in this group are guarded casts.}
\newcommand{\gGuardedDesc}{\gGuardedTableDesc}

\newcommand{\gAPITableDesc}{Cast patterns that depends on an API definition.}
\newcommand{\gAPIDesc}{\gAPITableDesc}

\newcommand{\gCovarianceTableDesc}{Patterns related to different kinds of covariance.}
\newcommand{\gCovarianceDesc}{\gCovarianceTableDesc}

\newcommand{\gGenericsTableDesc}{Patterns related to use or misuse of generics.}
\newcommand{\gGenericsDesc}{\gGenericsTableDesc}

\newcommand{\gTypeHackingTableDesc}{Casts due to hacking the type system.}
\newcommand{\gTypeHackingDesc}{\gTypeHackingTableDesc}

\newcommand{\gCodeSmellTableDesc}{The patterns in this group are regarded as code smells.}
\newcommand{\gCodeSmellDesc}{\gCodeSmellTableDesc}
